Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-07-28 tex/ms.tex
more results text, and figure captions

An example spectrum, both after and before spectrophotometric
calibration, is shown in Figure \ref{fig:data}.  When fitting the
spectra we mask the region around the bright OI5577 sky line, and we
fit only to the spectrum with $3750 < \lambda < 7200$ to avoid the low
S/N edges and, on the red side, imperfect sky line subtraction in a
region of the spectrum that has a paucity of informative spectral
lines.Furthermore, the MILES empirical spectra (see
\S\ref{sec:cluster_model}) are only available for $\lambda < 7500$\AA
{\color{red} Specify/Justify order of calibration polynomial here?}.

@@

We first infer the parameters of interest $\theta$ for a calibrated
spectrum of one of the clusters, \excluster, using the full YY-band
photometry. In Figure \ref{fig:inferred_spectrum} we show the spectra
that result from draws of the parameters $[\theta,\alpha]$ from the
posterior distribution, as well as several of the individual
components of the model constructed from each draw.  This figure also
shows the calibrated spectrum on which the priors were conditioned,
and residuals between the posterior models and the observed data.  In
Figure \ref{fig:inferred_sed} we also show the residuals between the
data and the draws from the posterior for the spectra. In Figure
\ref{fig:inferred_params} we show the marginalized and joint PDFs for
a subset of the full model parameters.

BDJ: Discuss degeneracies, etc.  Apparently we get really nice
redshift/velocity constraints for free.

BDJ: Next, we infer the parameters of the spectrum of the same cluster
\emph{without} spectrophotometric calibration.

BDJ: Then, we show select marginalized or joint PDFs for each cluster
calibrated/uncalibrated, to assess consistency.  They are very consistent.

@@

\begin{figure}[h!]
\includegraphics[width=0.5\textwidth]{figures/ptri_b192-g242_020_cal.png}
\caption{ Marginalized and joint PDFs of  subset of the physical
  parameters $\theta$ inferred from the spectophotometrically
  calibrated spectrum of \excluster. \label{fig:inferred_params}}
\end{figure}

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/cfig_b192-g242_020.png}
\caption{Show the calibration vector and our inference of it? \label{fig:inferred_calib}}
\end{figure*}

\begin{figure}[h!]
\caption{Money plot.  Show the difference between the parameters
  inferred from the calibrated and uncalibrated spectra, for each
  cluster.\label{fig:boom}}
\end{figure}

>>>>

An example spectrum, both after and before spectrophotometric
calibration, is shown in Figure \ref{fig:data}.  When fitting the
spectra we mask the region around the bright OI5577 sky line, and we
fit only to the spectrum with $3750 < \lambda < 7200$ to avoid the low
S/N edges and, on the red side, imperfect sky line subtraction in a
region of the spectrum that has a paucity of informative spectral
lines. Furthermore, the MILES spectral library (see
\S\ref{sec:cluster_model}) only extends to $\lambda < 7500$\AA.
{\color{red} Specify/Justify order of calibration polynomial here?}.

{\color{blue} DRW words about photometry}

@@

We first infer the parameters of interest $\theta$ for a calibrated
spectrum of one of the clusters, \excluster, using the full YY-band
photometry. In Figure \ref{fig:inferred_spectrum} we show the spectra
that result from draws of the parameters $[\theta,\alpha]$ from the
posterior distribution, as well as several of the individual
components of the model constructed from each draw. Figure
\ref{fig:inferred_spectrum} also shows the calibrated spectrum on
which the priors were conditioned, and residuals between the posterior
models and the observed data.  The agreement is quite good, though
some lines are not accurately predicted.  For example, the observed
Mg$b$ absorption appears stronger than the modeled absorption.

In Figure \ref{fig:inferred_sed} we show the corresponding SED for the
posterior parameter draws, compared to the observed SED. Finally, In
Figure \ref{fig:inferred_params} we show the marginalized and joint
PDFs for a subset of the full model parameters.

@@

\begin{figure}[h!]
\includegraphics[width=0.5\textwidth]{figures/ptri_b192-g242_020_cal.png}
\caption{ Marginalized and joint PDFs of  subset of the physical
  parameters $\theta$ inferred from the spectophotometrically
  calibrated spectrum of \excluster. The blue lines indicate the
  parameter values that resulted from the powell minimization. \label{fig:inferred_params}}
\end{figure}

The physical model parameters that we infer indicate that \excluster~
has super-solar metallicity, an age of $\sim 225$ Myr, moderate dust
extinction, and a stellar mass of $\sim 1e5$ M$_{sun}$ {\color{blue}
check that this is current mass, not initial mass}.  We find a spectral
broadening of $\sim 1.75$\AA (4.1\AA FWHM), which when combined in
quadrature with the intrinsic resolution of the MILES library, 2.5\AA
FWHM \citep{beifiori11}, reproduces the typical line-spread function
of the MMT Hectospec instrument, $\sim 5.0$\AA \citep{fabricant13}.
We obtain strong constraints on the systemic velocity.

For the calibration model, we obtain a calibration vector $f(\alpha)$
that is nearly linear in wavelength {\color{red} WHY IS IT NOT A
CONSTANT?  Need longer burn-in?  Is this the same issue as the SED
residuals?}.  The length scale of the Gaussian process is $\sim
60$\AA.  It is possible to reconstruct the inferred total
multiplicative calibration vector for each draw of the model
parameters.  Rearranging equation \ref{eq:spectroscopicLF} yields
\begin{eqnarray} 
\frac{d}{\mu(\theta)} & = & f(\alpha) +
\frac{\tilde{\Delta}}{\mu(\theta)}
\quad ,
\end{eqnarray}
for the total effective multiplicative calibration, where
$\tilde{\Delta}$ is now the Gaussian process mean prediction for the
residual between the data and the model. The inverse of this ratio is
shown in the left panel of Figure \ref{fig:inferred_calib} as our
inferred total multiplicative calibration function; if the
spectrophotometric calibration were perfect and we had correctly
inferred it, then we would expect this vector to be constant as a
function of wavelength.

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/cfig_b192-g242_020.png}
\caption{Left: Samples of the effective multiplicative calibration
  vector for the spectrophotometrically calibrated spectrum of
  \excluster~ ({\it cyan}) compared to that obtained from ancillary
  photometric data ({\it magenta}).  Right:  The same, but for the
  uncalibrated data. 
 \label{fig:inferred_calib}}
\end{figure*}

BDJ: Next, we infer the parameters of the spectrum of the same cluster
\emph{without} spectrophotometric calibration.  How many/which figures
to show?

BDJ: Then, we show select marginalized or joint PDFs for each cluster
calibrated/uncalibrated, to assess consistency.  Or we just show
comparisons of confidence intervals.

\begin{figure}[h!]
\includegraphics[width =0.5\textwidth]{figures/B192_020_cratio.pdf}
\caption{Money plot.  Show the difference between the parameters
  inferred from the calibrated and uncalibrated spectra, for each
  cluster. Tjis is a placeholder, since it only shows B192 for fixed
  GP parameters. \label{fig:boom}}
\end{figure}
